### 2016-03-22 docs/online_supporting_information.Rmd
breaks apart interaction SI table by vital rate

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
---

@@

df <- melt(unlist(vital_comp_list))
pieces <- strsplit(rownames(df), split = "[.]")
df$vitalrate <- sapply(pieces, "[", 1)
sites <- sapply(pieces, "[", 2)
df$site <- substr(sites, start = 1, stop = nchar(sites)-1)
df$interintra <- substr(sites, start = nchar(sites), stop = nchar(sites))
avg_interintra <- ddply(df, .(site, interintra), summarise,
                        avg_val = mean(value))
avg_interintra[which(avg_interintra$interintra==1),"interintra"] <- "Interspecific Competition"
avg_interintra[which(avg_interintra$interintra==2),"interintra"] <- "Intraspecific Competition"
interintra_table <- dcast(avg_interintra, site~interintra, value.var = "avg_val")

comp_cap <- "Average interaction coefficients across vital rates for each community."
print(xtable(interintra_table, caption = comp_cap),
  caption.placement="top",
  include.rownames = FALSE, 
  sanitize.colnames.function = identity,
  comment=FALSE)
```

>>>>

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: false
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
---

@@

df <- melt(unlist(vital_comp_list))
pieces <- strsplit(rownames(df), split = "[.]")
df$vitalrate <- sapply(pieces, "[", 1)
sites <- sapply(pieces, "[", 2)
df$site <- substr(sites, start = 1, stop = nchar(sites)-1)
df$interintra <- substr(sites, start = nchar(sites), stop = nchar(sites))

dftable <- dcast(df, site+interintra~vitalrate, value.var = "value")
colnames(dftable) <- c("Site", "Interaction Type", "Growth", "Recruitment", "Survival")
dftable[which(dftable$`Interaction Type`==1),"Interaction Type"] <- "Interspecific"
dftable[which(dftable$`Interaction Type`==2),"Interaction Type"] <- "Intraspecific"
# avg_interintra <- ddply(df, .(site, interintra), summarise,
#                         avg_val = mean(value))
# avg_interintra[which(avg_interintra$interintra==1),"interintra"] <- "Interspecific Competition"
# avg_interintra[which(avg_interintra$interintra==2),"interintra"] <- "Intraspecific Competition"
# interintra_table <- dcast(avg_interintra, site~interintra, value.var = "avg_val")

comp_cap <- "Average interaction coefficients for each vital rate for each community."
print(xtable(dftable, caption = comp_cap, digits=4),
  caption.placement="top",
  include.rownames = FALSE, 
  sanitize.colnames.function = identity,
  comment=FALSE)
```
